infercnv-consensus-cell-type Analysis

### 2025-03-19 analyses/infercnv-consensus-cell-type/notebook-template.Rmd
establish skeleton module

---
title: "cell-type-consensus Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-consensus")
```

>>>>

---
title: "infercnv-consensus-cell-type Analysis"
author:
  - Your name here
date: "`r Sys.Date()`"
output: html_notebook
---

@@

# The path to this module
module_base <- file.path(repository_base, "analyses", "infercnv-consensus-cell-type")
```
